Inpainting with dimensionality reduction in the Fourier domain

### 2011-06-20 project/Paper/paper.tex
Small stuff to allow pull again
+ Added gradient descent to paper

Therefore we tried different error function including both, the image error $E$, and the time $T$ spent. The image error here is the average
squared error of a reconstructed pixel to the original pixel, scaled with a factor (usually about 10000), while the time is measured in seconds.

@@

\subsubsection{Gradient descent}

>>>>

Therefore we tried different error function including both, the image error $E$, and the time $T$ spent (see table \ref{error_function_table}). The image error here is the average
squared error of a reconstructed pixel to the original pixel, scaled with a factor (usually about 10000), while the time is measured in seconds.

@@

% TODO maybe add 3d plot for some of the error functions

\subsubsection{Gradient descent}
The idea behind our gradient descent is to optimize all the parameters at once, instead of fine-tuning each of them separately. For that, we
calculate the derivative of the error function depending on one of our 10 parameters, and then move the parameter into the direction where the
error decreases fastest. We also consider the slope, and make big changes if the derivative is big, and small changes if the derivative is small.
Iteratively, we calculate all of the 10 derivatives, change all the parameters and start over again.

Since the error and time are measured, we cannot algebraically determine the gradient of the error function. Instead, we do a discrete estimation,
measuring the error with finite differences. The error for parameter values plus and minus a small delta, divided by two, gives us our estimated
derivative.

In figure \ref{}
